How the Practice of TDD Influences \\Class Design in Object-Oriented Systems: \\Patterns of Unit Tests Feedback

### 2012-12-22 sbes2012-english/paper.tex
revisao da marcela

When using TDD, a developer only writes code that is covered by a test. Due
to that, it is common to relate the practice of TDD to software testing. However,
a common discourse among TDD practitioners is regarding its effects on the internal code quality.
Many authors, well-known by industry and academia, such as Kent Beck \cite{TDDByExample}, 
Robert Martin \cite{agile-ppp}, Steve Freeman \cite{GOOS}, and Dave Astels \cite{astels-tdd}, 
state (without scientific evidence) that the practice of TDD promotes a significative
improvement on class design, helping developers to create more cohesive less coupled
classes.

@@

TDD is a software development practice that is based on a repetition of a small
cycle. First, developers write a failing test. Then, they make it pass,
by implementing the desired functionality. After that, they refactor the code
to remove code or data duplication that was generated by the process. Besides that,
simplicity is intrinsic to the process: the practitioner writes the simplest
test that fails and writes the simplest implementation that makes the
test pass. This cycle is also known as "Red-Green-Refactor", as it recalls the
colors that a developer usually sees when doing TDD: the red means that a test
is failing, and green means that the test passes successfully.

It is common to relate TDD to software testing practices. Although the creation
of tests is intrinsic to the process, it is also said that TDD helps developers
to create more flexible, cohesive, and less coupled classes \cite{tdd-taxonomy}. 
The tests are the tool used by developers to evaluate the class design that is being developed.
Therefore, many developers refers to TDD 
as \textit{Test-Driven Design} \cite{tdd-taxonomy}.

@@

In Table \ref{valores-separados}, we calculated the \textit{p-values} of the metric,
splliting them by experience in software development and TDD. The values for the group that
was experienced in TDD and not experienced in software development was not calculated as no
participant fitted on it.

@@

The majority of the participants also commented that one difference that is
perceived when they practice TDD is the constant feedback. In traditional testing,
the time between the production code writing and test code writing is too long.
When practicing TDD, developers are forced to write the test first, and receive all
feedback a test can give sooner.

@@

\begin{framed}
	\textit{"I take it as a rule: everytime it is very complex [the test],
	I think we should stop and refactor because, in my opinion, it can be simpler."}	
\end{framed}

@@

Also, the existence of the word \textit{"if"} in the name of test is another
pattern. Tests that contain a name like that usually indicate the existence
of an "if" in the production code. Those many conditions might be refactored and,
through the use of polymorphism, eliminated. We call it \textbf{Conditional in Test's name}.

>>>>

When using TDD, a developer only writes code that is covered by a test. Due
to that, it is common to relate the practice of TDD to software testing. However,
a common discourse among TDD practitioners is regarding its effects on the internal code quality.
Many authors well-known by industry and academia, such as Kent Beck \cite{TDDByExample}, 
Robert Martin \cite{agile-ppp}, Steve Freeman \cite{GOOS}, and Dave Astels \cite{astels-tdd}, 
state (without scientific evidence) that the practice of TDD promotes a significative
improvement on class design, helping developers to create more cohesive less coupled
classes.

@@

TDD is a software development practice that is based on a repetition of a small
cycle. First, developers write a failing test. Then, they make it pass,
by implementing the desired functionality. After that, they refactor the code
to remove code or data duplication that was generated by the process. Moreover,
simplicity is intrinsic to the process: the practitioner writes the simplest
test that fails and writes the simplest implementation that makes the
test pass. This cycle is also known as "Red-Green-Refactor", as it recalls the
colors that a developer usually sees when doing TDD: the red means that a test
is failing, and green means that the test passes successfully.

It is common to relate TDD to software testing practices. Although the creation
of tests is intrinsic to the process, it is also said that TDD helps developers
to create more flexible, cohesive, and less coupled classes \cite{tdd-taxonomy}. 
The tests are the tool used by developers to evaluate the class design that is being developed.
Therefore, many developers refer to TDD 
as \textit{Test-Driven Design} \cite{tdd-taxonomy}.

@@

In Table \ref{valores-separados}, we calculated the \textit{p-values} of the metric,
splitting them by experience in software development and TDD. The values for the group that
was experienced in TDD and not experienced in software development was not calculated as no
participant fitted on it.

@@

The majority of the participants also commented that one difference that is
perceived when they practice TDD is the constant feedback. In traditional testing,
the time between the production code writing and test code writing is too long.
When practicing TDD, developers are forced to write the test first, and receive all
feedback a test can provide sooner.

@@

\begin{framed}
	\textit{"I take it as a rule: every time it is very complex [the test],
	I think we should stop and refactor because, in my opinion, it can be simpler."}	
\end{framed}

@@

Also, the existence of the word \textit{"if"} in the name of the test is another
pattern. Tests that contain a name like that usually indicate the existence
of an "if" in the production code. Those many conditions might be refactored and,
through the use of polymorphism, eliminated. We call it \textbf{Conditional in Test's name}.
